## Basics

To run code from the script (the top right pane) in RStudio, you can:
* Highlight the code you want to run, then press `Ctrl + Enter`
* Click on a line of code in the script that you want to run to move your cursor there, then press `Ctrl + Enter`

To run code in the console (the bottom right pane), type in or paste what you want to run and press `Enter`.

# Variables
Use the `<-` operator create new variables.
When you do this, you basically assign a name a new R object, and it gets saved.
The name of the variable goes on the left,
and the variable's value(s) go on the right.
When you run the name of a variable in R, it will spit out the object that goes by that name.

```{r}
# assign to a number the name "x'
x <- 4
x  # should spit out 4

y <- "This is a string"
y  # should spit out the string saved to the name "y"
```

# Operators
R's arithmetic operators are the similar to other languages.
`+` adds, `-` subtracts, `*` multiplies, and `/` divides.
`^` is used for exponentiation.
Use parentheses if you need a specific order of operations

```{r}
x <- 6
y <- 3

x + y
x - y
x * y
x / y
x ^ y

```

R's logical operators are similar, too.
`<` is _less than_, `>` is _greater than_.
`<=` and `>=` are _less than or equal to_ and _greater than or equal to_, respectively.
`==` means _is equal to_. __THIS IS IMPORTANT TO REMEMBER.__
`!=` means _is not equal to_.

Using logical operators will return a `TRUE` or `FALSE` boolean.

```{r}
3 > 7
3 < 7
4 <= 2 ^ 2
10 >= 5 + 6
15 == 30 / 2

"apple" == "orange"  # strings can be compared, too
"b" != "a"

```


