## Basics

To run code from the script (the top right pane) in RStudio, you can:
* Highlight the code you want to run, then press `Ctrl + Enter`
* Click on a line of code in the script that you want to run to move your cursor there, then press `Ctrl + Enter`

To run code in the console (the bottom right pane), type in or paste what you want to run and press `Enter`.

# Variables
Use the `<-` operator create new variables.
When you do this, you basically assign a name a new R object, and it gets saved.
The name of the variable goes on the left,
and the variable's value(s) go on the right.
When you run the name of a variable in R, it will spit out the object that goes by that name.

```{r}
# assign to a number the name "x'
x <- 4
x  # should spit out 4

y <- "This is a string"
y  # should spit out the string saved to the name "y"
```

# Operators
R's arithmetic operators are the similar to other languages.
`+` adds, `-` subtracts, `*` multiplies, and `/` divides.
`^` is used for exponentiation.
Use parentheses if you need a specific order of operations

```{r}
x <- 6
y <- 3

x + y
x - y
x * y
x / y
x ^ y

```

R's logical operators are similar, too.
`<` is _less than_, `>` is _greater than_.
`<=` and `>=` are _less than or equal to_ and _greater than or equal to_, respectively.
`==` means _is equal to_. __THIS IS IMPORTANT TO REMEMBER.__
`!=` means _is not equal to_.

Using logical operators will return a `TRUE` or `FALSE` boolean.

```{r}
3 > 7
3 < 7
4 <= 2 ^ 2
10 >= 5 + 6
15 == 30 / 2

"apple" == "orange"  # strings can be compared, too
"b" != "a"

```

## Functions
Functions carry out tasks, often taking arguments/parameters as inputs and returning an object as an output.
Functions all have a similar format:

```{r, eval = FALSE}
functionName(arg_list) 
```

Functions have a name, followed by parentheses.
Functions often require input(s), which go in the parentheses. These are arguments.
When you _specify_ a function's arguments, you're giving it the inputs that it needs.

Here's an example of a function:

```{r, eval = FALSE}
read.csv(file = "dataset.csv", header = TRUE)
```

The function is called `read.csv()`.
It imports a CSV file into R.
The main arguments of `read.csv()` are `file` and `header`.
The `file` argument is where you supply the name of the CSV file,
and the `header` argument tells R whether the first line in the CSV file contains column names, or not.

As it is, the function above would simply read the CSV file, and then show you the result.
If you want to save the read-in CSV file into your R workspace, so you can do things to it,
you should assign it a name:

```{r, eval = FALSE}
my_data <- read.csv(file = "dataset.csv", header = TRUE)
```

A lot of functions have arguments that you can specify, without having to explicitly type out the arguments' name.
For example, we can omit the `file =` from our  `read.csv()` function--
it's smart enough to know that the string we give it in the first argument spot is the CSV file's name.
Knowing what argument names can be ommitted comes with experience, for the most part.

```{r, eval = FALSE}
# the function knows that the first input is the file name
my_data <- read.csv("dataset.csv", header = TRUE)
```

Some arguments require including the name and `=` before specifying them, to prevent ambiguous inputs.
We can't omit the `header =` in our `read.csv()` function above, for example, 
because `read.csv()` has other arguments that take `TRUE` or `FALSE` as an input.
It wouldn't know what argument a lone `TRUE` should apply to.

A lot of functions have arguments have default values.
If you don't specify an argument that has a default value,
the function will go ahead and use the default value to specify that argument.

For example: The default value for the `header` argument in `read.csv()` is `FALSE`,
meaning that if you don't specify the `header` argument yourself,
the `read.csv()` function will assume that your CSV file has no header row.

```{r, eval = FALSE}
# header = FALSE is implied here, by default
my_data <- read.csv("dataset.csv")
```
